Energy stable discontinuous Galerkin formulations using discrete differential operators

### 2017-05-16 docs/splitform/main.tex
updating splitform

Lifting operators and discrete gradients \cite{bassi1997high, di2011mathematical}

Goal: reduce aliasing in advective problems caused by variable coefficients and curvilinear or non-affine mappings.

>>>>

Lifting operators and discrete gradients \cite{bassi1997high, di2011mathematical}.

Goal: reduce aliasing in advective problems caused by variable coefficients and curvilinear or non-affine mappings.  Resembles ideas from summation by parts \cite{olsson1995summation1, olsson1995summation2, hicken2016multidimensional}, but based on global DG differentiation operators.
